### 2016-01-23 project/paper/appendices/sparql.tex
Byzantine errors

>>>>

Apart from the language problem there seem to be Byzantine problems that are really weird. We don't have an explation nor a soltion to address these problems.

\begin{enumerate}
\item \textbf{Links are not broken but queries on them don't work}\\
Take for example the following person Paul Rübig. There is an data item about him on DBpedia:  \url{http://dbpedia.org/page/Paul\_ R\"ubig}. But if you query this specific resource with the query in listing \ref{lst:dbpedia} you will not get any results.
\lstinputlisting[language=SQL, caption=Query that doesn't work, label={lst:dbpedia}]{dbpedia.rq}
\end{enumerate}
